Paper Figures and Text

### 2023-01-11 Fish Data Analysis/Paper_Figures.qmd
Adding group number finding
Also added the code that was used to make and test it to "Old Code"

@@

eight_fish_all_cond
eight_fish_still_model
eight_fish_flow_model
```

@@

dark_eight_and_single_graph <- ggplot(dark_eight_and_single_sum,
                           aes(x = Fish_Num_Ratio, y = turn_bool, color = Type))+
  geom_line(aes(x = Fish_Num_Ratio, y = predicted, color = Type)) +
  geom_point(aes(x = Fish_Num_Ratio, y = predicted, color = Type, size = n)) +
  theme_classic() +
  xlab("# Fish on Left : # Fish on Right") +
  ylab("Probability of a Right Turn") +
  ylim(0,1) +
  #ggtitle("GLM Model of the Probability of a Right Turn Darkness for Eight or Single Fish") +
  scale_colour_manual(values = c(sim_color,dark_no_ab_color)) +
  scale_size_continuous(breaks = c(25,50,75)) +
  scale_x_continuous(breaks = c(0,0.125,0.25,0.375,
                                0.5,0.625,0.75,0.875),
                     labels = c("7:0","6:1","5:2","4:3",
                                "3:4","2:5","1:6","0:7")) + 
  labs(size = "Number of Turns")

@@

ablation_eight_and_single_graph <- ggplot(ablation_eight_and_single_sum,
                           aes(x = Fish_Num_Ratio, y = turn_bool, color = Type))+
  geom_line(aes(x = Fish_Num_Ratio, y = predicted, color = Type)) +
  geom_point(aes(x = Fish_Num_Ratio, y = predicted, color = Type, size = n)) +
  theme_classic() +
  xlab("# Fish on Left : # Fish on Right") +
  ylab("Probability of a Right Turn") +
  ylim(0,1) +
  #ggtitle("GLM Model of the Probability of a Right Turn Ablated for Eight or Single Fish") +
  scale_colour_manual(values = c(sim_color,light_ab_color)) +
  scale_size_continuous(breaks = c(25,50,75)) +
  scale_x_continuous(breaks = c(0,0.125,0.25,0.375,
                                0.5,0.625,0.75,0.875),
                     labels = c("7:0","6:1","5:2","4:3",
                                "3:4","2:5","1:6","0:7"))+ 
  labs(size = "Number of Turns")

@@

light_eight_and_single_graph <- ggplot(light_eight_and_single_sum,
                           aes(x = Fish_Num_Ratio, y = turn_bool, color = Type))+
  geom_line(aes(x = Fish_Num_Ratio, y = predicted, color = Type)) +
  geom_point(aes(x = Fish_Num_Ratio, y = predicted, color = Type, size = n)) +
  theme_classic() +
  xlab("# Fish on Left : # Fish on Right") +
  ylab("Probability of a Right Turn") +
  ylim(0,1) +
  #ggtitle("GLM Model of the Probability of a Right Turn Light for Eight or Single Fish") +
  scale_colour_manual(values = c(sim_color,light_no_ab_color)) +
  scale_size_continuous(breaks = c(25,50,75)) +
  scale_x_continuous(breaks = c(0,0.125,0.25,0.375,
                                0.5,0.625,0.75,0.875),
                     labels = c("7:0","6:1","5:2","4:3",
                                "3:4","2:5","1:6","0:7"))+ 
  labs(size = "Number of Turns")

light_eight_and_single_graph
ablation_eight_and_single_graph
dark_eight_and_single_graph
```

@@

school_data <- school_data %>% mutate(Flow = ifelse(Flow == "0", "Still Water", "Flowing Water (2 BL/s)")) %>%
                           mutate(Ablation = ifelse(Ablation == "N", "No Ablation", "Ablated")) %>%
                           mutate(Darkness = ifelse(Darkness == "N", "Light", "Dark")) %>%
                           filter(School_Speed < 7) %>%
                           mutate(Flow = factor(Flow), Ablation = factor(Ablation), Darkness = factor(Darkness)) %>%
                           mutate(Flow = fct_relevel(Flow, c("Still Water","Flowing Water (2 BL/s)"))) %>%
                           mutate(Ablation = fct_relevel(Ablation, c("No Ablation","Ablated"))) %>%
                           mutate(Darkness = fct_relevel(Darkness, c("Light","Dark"))) %>%
                           mutate(Flow_Ablation_Darkness = factor(paste(Flow,Ablation,Darkness,sep=", "))) %>%
                           group_by(Flow_Ablation_Darkness) %>%
                           mutate(NND_Mean_Val = mean(NND), NND_SD_Val = sd(NND),
                                  Polar_Mean_Val = mean(School_Polar), Polar_SD_Val = sd(School_Polar),
                                  Speed_Mean_Val = mean(School_Speed), Speed_SD_Val = sd(School_Speed)) %>%
                           ungroup()
```

@@

speed_still <- ggplot(school_data %>% filter(Flow == "Still Water"),
       aes(x = interaction(Ablation,Darkness,sep=", "), y = School_Speed,
           color = interaction(Ablation,Darkness,sep=", "),
           fill = interaction(Ablation,Darkness,sep=", ")))+
  stat_dots(side = "both", binwidth = unit(dot_binwidth, "npc")) +
  geom_point(aes(y = Speed_Mean_Val), size = 5, color = "Black") +
  geom_errorbar(aes(ymin=Speed_Mean_Val-Speed_SD_Val, ymax=Speed_Mean_Val+Speed_SD_Val), width=.2, color = "Black")+
  guides(fill = guide_legend(title = "Condition")) +
  scale_fill_manual(values=c(light_no_ab_color, light_ab_color, dark_no_ab_color)) +
  scale_color_manual(values=c(light_no_ab_color, light_ab_color, dark_no_ab_color)) +
  #ggtitle("Effect of Available Senses on Speed (BL/s) in Still Water") +
  xlab("") +
  ylab("Speed (BL/s)") +
  theme_light()+ 
  theme(legend.position = "none") +
  ylim(0,8.5)+
  stat_compare_means(comparisons = my_comparisons, label = "p.signif", hide.ns = TRUE) +
  theme(axis.text.x = element_text(size = 15),
        axis.text.y = element_text(size = 15),
        axis.title.y = element_text(size = 15))

@@

speed_still
speed_flow
```
### Now we combine them

@@

velocity_cor_data_sum <- velocity_cor_data %>% mutate(round_Distance = factor(round_any(Distance,2))) %>%
                                               filter(Flow == "Still Water") %>%
                                               group_by(round_Distance,Flow_Ablation_Darkness) %>%
                                               summarise(mean_Speed_Diff = mean(abs(Speed_Diff)),
                                                         sd_Speed_Diff = sd(abs(Speed_Diff)),
                                                         mean_Spatial_Auto = mean(abs(Spatial_Auto)),
                                                         sd_Spatial_Auto = sd(abs(Spatial_Auto))) %>%
                                               ungroup()
```

@@

ggplot(velocity_cor_data_sum, aes(x = round_Distance, y = mean_Spatial_Auto, color = Flow_Ablation_Darkness))+
  geom_point(position=position_dodge(width = 0.6))+
  geom_errorbar(aes(ymin = mean_Spatial_Auto-sd_Spatial_Auto, ymax = mean_Spatial_Auto+sd_Spatial_Auto),
                position=position_dodge(width = 0.6))+
  scale_color_manual(values=c(light_no_ab_color, light_ab_color, dark_no_ab_color)) +
  theme_classic()
```

@@

>>>>

eight_fish_all_cond_one_chart <- ggplot(turning_data_sum %>% filter(Flow == "Still Water") %>% filter(Type == "Eight Fish"),
                           aes(x = Fish_Num_Ratio, y = mean_right_turn, color = Flow_Ablation_Darkness))+
  geom_point()+
  geom_line(alpha = 0.25) +
  theme_classic() +
  xlab("# Fish on Left : # Fish on Right") +
  ylab("Probability of a Right Turn") +
  #ggtitle("GLM Model of the Probability of a Right Turn in Still Water") +
   ylim(0,1) +
  scale_colour_manual(values = c(light_no_ab_color,light_ab_color,dark_no_ab_color)) +
  scale_x_continuous(breaks = c(0,0.125,0.25,0.375,
                                0.5,0.625,0.75,0.875),
                     labels = c("7:0","6:1","5:2","4:3",
                                "3:4","2:5","1:6","0:7"))+ 
  labs(color = "Sensory Conditions")

@@

eight_fish_all_cond
eight_fish_still_model
eight_fish_flow_model

eight_fish_all_cond_one_chart
```

@@

dark_eight_and_single_graph <- ggplot(dark_eight_and_single_sum,
                           aes(x = Fish_Num_Ratio, y = turn_bool, color = Type))+
  geom_line(aes(x = Fish_Num_Ratio, y = predicted, color = Type)) +
  geom_point(aes(x = Fish_Num_Ratio, y = predicted, color = Type)) +
  theme_classic() +
  xlab("# Fish on Left : # Fish on Right") +
  ylab("Probability of a Right Turn") +
  ylim(0,1) +
  #ggtitle("GLM Model of the Probability of a Right Turn Darkness for Eight or Single Fish") +
  scale_colour_manual(values = c(sim_color,dark_no_ab_color)) +
  #scale_size_continuous(breaks = c(25,50,75)) +
  scale_x_continuous(breaks = c(0,0.125,0.25,0.375,
                                0.5,0.625,0.75,0.875),
                     labels = c("7:0","6:1","5:2","4:3",
                                "3:4","2:5","1:6","0:7")) + 
  labs(size = "Number of Turns")

dark_eight_and_single_graph_real <- ggplot(turning_data_sum %>% filter(Flow_Ablation_Darkness == "Still Water, No Ablation, Dark"),
                           aes(x = Fish_Num_Ratio, y = mean_right_turn, color = Type))+
  geom_point()+
  geom_line(alpha = 0.25) +
  theme_classic() +
  xlab("# Fish on Left : # Fish on Right") +
  ylab("Probability of a Right Turn") +
  #ggtitle("GLM Model of the Probability of a Right Turn in Still Water") +
   ylim(0,1) +
  scale_colour_manual(values = c(sim_color,dark_no_ab_color)) +
  scale_x_continuous(breaks = c(0,0.125,0.25,0.375,
                                0.5,0.625,0.75,0.875),
                     labels = c("7:0","6:1","5:2","4:3",
                                "3:4","2:5","1:6","0:7"))+ 
  labs(color = "Sensory Conditions")

@@

ablation_eight_and_single_graph <- ggplot(ablation_eight_and_single_sum,
                           aes(x = Fish_Num_Ratio, y = turn_bool, color = Type))+
  geom_line(aes(x = Fish_Num_Ratio, y = predicted, color = Type)) +
  geom_point(aes(x = Fish_Num_Ratio, y = predicted, color = Type)) +
  theme_classic() +
  xlab("# Fish on Left : # Fish on Right") +
  ylab("Probability of a Right Turn") +
  ylim(0,1) +
  #ggtitle("GLM Model of the Probability of a Right Turn Ablated for Eight or Single Fish") +
  scale_colour_manual(values = c(sim_color,light_ab_color)) +
  #scale_size_continuous(breaks = c(25,50,75)) +
  scale_x_continuous(breaks = c(0,0.125,0.25,0.375,
                                0.5,0.625,0.75,0.875),
                     labels = c("7:0","6:1","5:2","4:3",
                                "3:4","2:5","1:6","0:7"))+ 
  labs(size = "Number of Turns")

@@

light_eight_and_single_graph <- ggplot(light_eight_and_single_sum,
                           aes(x = Fish_Num_Ratio, y = turn_bool, color = Type))+
  geom_line(aes(x = Fish_Num_Ratio, y = predicted, color = Type)) +
  geom_point(aes(x = Fish_Num_Ratio, y = predicted, color = Type)) +
  theme_classic() +
  xlab("# Fish on Left : # Fish on Right") +
  ylab("Probability of a Right Turn") +
  ylim(0,1) +
  #ggtitle("GLM Model of the Probability of a Right Turn Light for Eight or Single Fish") +
  scale_colour_manual(values = c(sim_color,light_no_ab_color)) +
  #scale_size_continuous(breaks = c(25,50,75)) +
  scale_x_continuous(breaks = c(0,0.125,0.25,0.375,
                                0.5,0.625,0.75,0.875),
                     labels = c("7:0","6:1","5:2","4:3",
                                "3:4","2:5","1:6","0:7"))+ 
  labs(size = "Number of Turns")

light_eight_and_single_graph
ablation_eight_and_single_graph
dark_eight_and_single_graph

dark_eight_and_single_graph_real
```

@@

school_data <- school_data %>% mutate(Flow = ifelse(Flow == "0", "Still Water", "Flowing Water (2 BL/s)")) %>%
                           mutate(Ablation = ifelse(Ablation == "N", "No Ablation", "Ablated")) %>%
                           mutate(Darkness = ifelse(Darkness == "N", "Light", "Dark")) %>%
                           filter(School_Speed < 7) %>%
                           mutate(Flow = factor(Flow), Ablation = factor(Ablation), Darkness = factor(Darkness)) %>%
                           mutate(Flow = fct_relevel(Flow, c("Still Water","Flowing Water (2 BL/s)"))) %>%
                           mutate(Ablation = fct_relevel(Ablation, c("No Ablation","Ablated"))) %>%
                           mutate(Darkness = fct_relevel(Darkness, c("Light","Dark"))) %>%
                           mutate(Flow_Ablation_Darkness = factor(paste(Flow,Ablation,Darkness,sep=", "))) %>%
                           group_by(Flow_Ablation_Darkness) %>%
                           mutate(NND_Mean_Val = mean(NND), NND_SD_Val = sd(NND),
                                  Polar_Mean_Val = mean(School_Polar), Polar_SD_Val = sd(School_Polar),
                                  Speed_Mean_Val = mean(School_Speed), Speed_SD_Val = sd(School_Speed),
                                  Area_Mean_Val = mean(Area), Area_SD_Val = sd(Area)) %>%
                           ungroup()
```

@@

speed_still <- ggplot(school_data %>% filter(Flow == "Still Water"),
       aes(x = interaction(Ablation,Darkness,sep=", "), y = School_Speed,
           color = interaction(Ablation,Darkness,sep=", "),
           fill = interaction(Ablation,Darkness,sep=", ")))+
  stat_dots(side = "both", binwidth = unit(dot_binwidth, "npc")) +
  geom_point(aes(y = Speed_Mean_Val), size = 5, color = "Black") +
  geom_errorbar(aes(ymin=Speed_Mean_Val-Speed_SD_Val, ymax=Speed_Mean_Val+Speed_SD_Val), width=.2, color = "Black")+
  guides(fill = guide_legend(title = "Condition")) +
  scale_fill_manual(values=c(light_no_ab_color, light_ab_color, dark_no_ab_color)) +
  scale_color_manual(values=c(light_no_ab_color, light_ab_color, dark_no_ab_color)) +
  #ggtitle("Effect of Available Senses on Speed (BL/s) in Still Water") +
  xlab("") +
  ylab("Speed (BL/s)") +
  theme_light()+ 
  theme(legend.position = "none") +
  ylim(-0.1,8.5)+
  stat_compare_means(comparisons = my_comparisons, label = "p.signif", hide.ns = TRUE) +
  theme(axis.text.x = element_text(size = 15),
        axis.text.y = element_text(size = 15),
        axis.title.y = element_text(size = 15))

@@

speed_still
speed_flow
```
### Area

area_still <- ggplot(school_data %>% filter(Flow == "Still Water"),
       aes(x = interaction(Ablation,Darkness,sep=", "), y = Area,
           color = interaction(Ablation,Darkness,sep=", "),
           fill = interaction(Ablation,Darkness,sep=", ")))+
  stat_dots(side = "both", binwidth = unit(dot_binwidth, "npc")) +
  geom_point(aes(y = Area_Mean_Val), size = 5, color = "Black") +
  geom_errorbar(aes(ymin=Area_Mean_Val-Area_SD_Val, ymax=Area_Mean_Val+Area_SD_Val), width=.2, color = "Black")+
  guides(fill = guide_legend(title = "Condition")) +
  scale_fill_manual(values=c(light_no_ab_color, light_ab_color, dark_no_ab_color)) +
  scale_color_manual(values=c(light_no_ab_color, light_ab_color, dark_no_ab_color)) +
  #ggtitle("Effect of Available Senses on Speed (BL/s) in Still Water") +
  xlab("") +
  ylab("Area (BL^2)") +
  theme_light()+ 
  theme(legend.position = "none") +
  #ylim(0,8.5)+
  stat_compare_means(comparisons = my_comparisons, label = "p.signif", hide.ns = TRUE) +
  theme(axis.text.x = element_text(size = 15),
        axis.text.y = element_text(size = 15),
        axis.title.y = element_text(size = 15))

area_flow <- ggplot(school_data %>% filter(Flow == "Flowing Water (2 BL/s)"),
       aes(x = interaction(Ablation,Darkness,sep=", "), y = Area,
           color = interaction(Ablation,Darkness,sep=", "),
           fill = interaction(Ablation,Darkness,sep=", ")))+
  stat_dots(side = "both", binwidth = unit(dot_binwidth, "npc")) +
  geom_point(aes(y = Area_Mean_Val), size = 5, color = "Black") +
  geom_errorbar(aes(ymin=Area_Mean_Val-Area_SD_Val, ymax=Area_Mean_Val+Area_SD_Val), width=.2, color = "Black")+
  guides(fill = guide_legend(title = "Condition")) +
  scale_fill_manual(values=c(light_no_ab_color, light_ab_color, dark_no_ab_color)) +
  scale_color_manual(values=c(light_no_ab_color, light_ab_color, dark_no_ab_color)) +
  #ggtitle("Effect of Available Senses on Speed (BL/s) in Still Water") +
  xlab("") +
  ylab("Area (BL^2)") +
  theme_light()+ 
  theme(legend.position = "none") +
  #ylim(0,8.5)+
  stat_compare_means(comparisons = my_comparisons, label = "p.signif", hide.ns = TRUE) +
  theme(axis.text.x = element_text(size = 15),
        axis.text.y = element_text(size = 15),
        axis.title.y = element_text(size = 15))

area_still
area_flow
```

```{r}
ggplot(school_data %>% filter(Flow == "Still Water"), 
       aes(x = NND, y = Area, color = interaction(Ablation,Darkness,sep=", ")))+
  geom_point()+
  #geom_smooth(method = "glm", formula = 'y ~ poly(x, 2)', se = FALSE)+
  geom_smooth(method = "gam", se = FALSE)+
  theme_classic()+
  guides(color = guide_legend(title = "Condition")) +
  scale_color_manual(values=c(light_no_ab_color, light_ab_color, dark_no_ab_color)) +
  xlab("NND (BL)")+
  ylab("Area (BL^2)")

### Now we combine them

@@

velocity_cor_data_sum <- velocity_cor_data %>% mutate(round_Distance = factor(round_any(Distance,0.1))) %>%
                                               filter(Flow == "Still Water") %>%
                                               group_by(round_Distance,Flow_Ablation_Darkness) %>%
                                               summarise(mean_Speed_Diff = mean(abs(Speed_Diff)),
                                                         sd_Speed_Diff = sd(abs(Speed_Diff)),
                                                         mean_Spatial_Auto = mean(Spatial_Auto),
                                                         sd_Spatial_Auto = sd(Spatial_Auto),
                                                         count = n()) %>%
                                               ungroup() %>%
                                               mutate(round_Distance = as.numeric(levels(round_Distance))[round_Distance]) %>%
                                               filter(count > 5)
```

@@

ggplot(velocity_cor_data_sum, aes(x = round_Distance, y = mean_Spatial_Auto, color = Flow_Ablation_Darkness))+
  geom_point(position=position_dodge(width = 0.6))+
  geom_smooth(method = "glm", se = FALSE, color = "black")+
  #geom_errorbar(aes(ymin = mean_Spatial_Auto-sd_Spatial_Auto, ymax = mean_Spatial_Auto+sd_Spatial_Auto),
  #              position=position_dodge(width = 0.6))+
  scale_color_manual(values=c(light_no_ab_color, light_ab_color, dark_no_ab_color)) +
  facet_wrap(~Flow_Ablation_Darkness)+
  theme_classic()
```

@@

## Startle Conditions
```{r}

startle_school_data <- read.csv("Data/Startle_First_Half_Fish_School_Values.csv")
startle_school_data <- na.omit(startle_school_data)

startle_school_data <- startle_school_data %>% mutate(Flow = ifelse(Flow == "0", "Still Water", "Flowing Water (2 BL/s)")) %>%
                           mutate(Ablation = ifelse(Ablation == "N", "No Ablation", "Ablated")) %>%
                           mutate(Darkness = ifelse(Darkness == "N", "Light", "Dark")) %>%
                           filter(School_Speed < 7) %>%
                           mutate(Flow = factor(Flow), Ablation = factor(Ablation), Darkness = factor(Darkness)) %>%
                           mutate(Flow = fct_relevel(Flow, c("Still Water","Flowing Water (2 BL/s)"))) %>%
                           mutate(Ablation = fct_relevel(Ablation, c("No Ablation","Ablated"))) %>%
                           mutate(Darkness = fct_relevel(Darkness, c("Light","Dark"))) %>%
                           mutate(Flow_Ablation_Darkness = factor(paste(Flow,Ablation,Darkness,sep=", "))) %>%
                           group_by(Flow_Ablation_Darkness) %>%
                           mutate(NND_Mean_Val = mean(NND), NND_SD_Val = sd(NND),
                                  Polar_Mean_Val = mean(School_Polar), Polar_SD_Val = sd(School_Polar),
                                  Speed_Mean_Val = mean(School_Speed), Speed_SD_Val = sd(School_Speed),
                                  Area_Mean_Val = mean(Area), Area_SD_Val = sd(Area)) %>%
                           ungroup() %>% 
                           mutate(Exp_Label = paste0("Darkness Pre-Startle ",Trial))

startle_school_data_light <- school_data %>% filter(Darkness == "Light" & Ablation == "No Ablation" & Flow == "Still Water") %>%
                                             mutate(Exp_Label = "Light")

startle_school_data <- rbind(startle_school_data_light,startle_school_data) %>% 
                       mutate(Exp_Label = factor(Exp_Label)) %>%
                       mutate(Exp_Label = fct_relevel(Exp_Label,c("Light",
                                                                  "Darkness Pre-Startle 1",
                                                                  "Darkness Pre-Startle 5",
                                                                  "Darkness Pre-Startle 30")))

my_comparisons <- list(c("Light", "Darkness Pre-Startle 1"), c("Light", "Darkness Pre-Startle 5"), c("Light", "Darkness Pre-Startle 30"))

nnd_startle <- ggplot(startle_school_data,
       aes(x = Exp_Label, y = NND,
           color = interaction(Ablation,Darkness,sep=", "),
           fill = interaction(Ablation,Darkness,sep=", ")))+
  stat_dots(side = "both", binwidth = unit(dot_binwidth, "npc")) +
  geom_point(aes(y = NND_Mean_Val), size = 3, color = "Black") +
  geom_errorbar(aes(ymin=NND_Mean_Val-NND_SD_Val, ymax=NND_Mean_Val+NND_SD_Val), width=.2, color = "Black")+
  guides(fill = guide_legend(title = "Condition")) +
  scale_fill_manual(values=c(light_no_ab_color, dark_no_ab_color, dark_no_ab_color)) +
  scale_color_manual(values=c(light_no_ab_color, dark_no_ab_color, dark_no_ab_color)) +
  #ggtitle("Effect of Available Senses on Nearest Neighbor Distance (NND) in Still Water") +
  xlab("") +
  ylab("NND (BL)") +
  theme_light()+ 
  theme(legend.position = "none") +
  #ylim(0,3)+
  stat_compare_means(comparisons = my_comparisons, label = "p.signif", hide.ns = TRUE) +
  theme(axis.text.x = element_text(size = 15),
        axis.text.y = element_text(size = 15),
        axis.title.y = element_text(size = 15))

polar_startle <- ggplot(startle_school_data,
       aes(x = Exp_Label, y = School_Polar,
           color = interaction(Ablation,Darkness,sep=", "),
           fill = interaction(Ablation,Darkness,sep=", ")))+
  stat_dots(side = "both", binwidth = unit(dot_binwidth, "npc")) +
  geom_point(aes(y = Polar_Mean_Val), size = 5, color = "Black") +
  geom_errorbar(aes(ymin=Polar_Mean_Val-Polar_SD_Val, ymax=Polar_Mean_Val+Polar_SD_Val), width=.2, color = "Black")+
  guides(fill = guide_legend(title = "Condition")) +
  scale_fill_manual(values=c(light_no_ab_color, dark_no_ab_color, dark_no_ab_color)) +
  scale_color_manual(values=c(light_no_ab_color, dark_no_ab_color, dark_no_ab_color)) +
  #ggtitle("Effect of Available Senses on Polarization in Still Water") +
  xlab("") +
  ylab("Polarization") +
  theme_light()+ 
  theme(legend.position = "none") +
  #ylim(0,1.15)+
  stat_compare_means(comparisons = my_comparisons, label = "p.signif", hide.ns = TRUE) +
  theme(axis.text.x = element_text(size = 15),
        axis.text.y = element_text(size = 15),
        axis.title.y = element_text(size = 15))

speed_startle <- ggplot(startle_school_data,
       aes(x = Exp_Label, y = School_Speed,
           color = interaction(Ablation,Darkness,sep=", "),
           fill = interaction(Ablation,Darkness,sep=", ")))+
  stat_dots(side = "both", binwidth = unit(dot_binwidth, "npc")) +
  geom_point(aes(y = Speed_Mean_Val), size = 5, color = "Black") +
  geom_errorbar(aes(ymin=Speed_Mean_Val-Speed_SD_Val, ymax=Speed_Mean_Val+Speed_SD_Val), width=.2, color = "Black")+
  guides(fill = guide_legend(title = "Condition")) +
  scale_fill_manual(values=c(light_no_ab_color, dark_no_ab_color, dark_no_ab_color)) +
  scale_color_manual(values=c(light_no_ab_color, dark_no_ab_color, dark_no_ab_color)) +
  #ggtitle("Effect of Available Senses on Speed (BL/s) in Still Water") +
  xlab("") +
  ylab("Speed (BL/s)") +
  theme_light()+ 
  theme(legend.position = "none") +
  #ylim(0,8.5)+
  stat_compare_means(comparisons = my_comparisons, label = "p.signif", hide.ns = TRUE) +
  theme(axis.text.x = element_text(size = 15),
        axis.text.y = element_text(size = 15),
        axis.title.y = element_text(size = 15))

nnd_startle
polar_startle
speed_startle

ggsave("Paper Figures/startle_nnd.png", nnd_startle, width = 12, height = 7)
